---
title: "Untitled"
author: "Reed Magleby"
date: "November 20, 2018"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

1. Write a function that calculates cumulative distribution function of a binomial random variable.
Compare results from your function with pbinom() function.

```{r}
binom_func <- function(x, size, p) {
  binom <- vector(length = x)
  for (i in (1:x)) {
    binom[i] <- (p^i) * (1 - p)^(size - i) * (factorial(size) / (factorial(i) * factorial(size - i)))
  }
  return(sum(binom))
}

binom_func(5, 10, 0.5)
pbinom(5, 10, 0.5)
```


2. Write a function that runs simulations to obtain power from a one-sample t-test. Run your function
(with number of simulations = 10,000 ) with n = 30, delta = 0.5, sd = 1 and sig.level = 0.05. Compare
your results with power.t.test(n = 30, delta = 0.5, sd = 1, sig.level = 0.05, type = 'one.sample').

```{r}

power_t <- function(n, delta, sd, alpha) {
  samples <- replicate(10000, {
    x <- rnorm(n = n, mean = delta, sd = sd)
    return(as.numeric(t.test(x)$p.value < alpha))
  })
  return(mean(samples))
}

power_t(n = 30, sd = 1, delta = 0.5, alpha = 0.05)
power.t.test(n = 30, delta = 0.5, sd = 1, sig.level = 0.05, type = "one.sample")$power
```


